### 2019-07-13 thesis.tex
agora vai

Plasma is a gas in which the atoms -or molecules- are in an ionized state.
In such condition, long-range electric and magnetic forces determine the
interactions of the charged particles. This coupling between the variations
in the electric and magnetic fields and the motion of ions and electrons
gives rise to the myriad of collective processes that characterize a
plasma\cite{tsytotp}.

>>>>

In this thesis, we present a theoretical model for the inclusion of single
particle fluctuations and collisional processes related to electrostatic
oscillation in rarefied, unmagnetized, non-relativistic and fully ionized
plasmas.

% Plasma is a gas in which the atoms -or molecules- are in an ionized state.
% In such condition, long-range electric and magnetic forces determine the
% interactions of the charged particles. This coupling between the variations
% in the electric and magnetic fields and the motion of ions and electrons
% is behind the collective behavior that characterizes the plasma dynamics
% \cite{tsytotp}. The complex processes
